---
title: "Process CATegories data"
author: "Martin Zettersten"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

## Load packages

```{r setup, message=FALSE}
library(tidyverse)
library(janitor)
library(here)
library(readxl)
library(assertthat)
library(tools)

knitr::opts_chunk$set(cache = FALSE, warn = FALSE,warning=FALSE, message = FALSE)
```

```{r global_params}
ms_per_frame <- 1000/30 #target frame rate
skip_frames <- 0 # how many frames were skipped at the beginning of each video
looking_data_path <- here::here("..","..","data","processed_data","CATegories_exp2_peyecoder_data_anonymized.csv")
processed_subj_path <- here::here("..","..","data","processed_data","CATegories_exp2_processed_participant_data_anonymized.csv")
frame_data_path <- here::here("..","..","data","processed_data","CATegories_exp2_processed_frame_data.csv")
frame_rate_info_path <- here::here("..","..","data","processed_data","frame_rate_tables")
survey_path <- here::here("..","..","data","processed_data","CATegories_exp2_processed_survey_data.csv")
write_path <- here::here("..","..","data","processed_data","CATegories_exp2_processed_data.csv")
write_path_rds <- here::here("..","..","data","processed_data","CATegories_exp2_processed_data.rds")
```

## Load coded looking data

First, we load in the coded video data output from peyecoder (https://pypi.org/project/peyecoder/), pre-processed into a single data file in long format.

```{r load_data}
d <- read_csv(looking_data_path)
```

Additional clean-up: Here, we do any extra clean-up to file entries to facilitate later processing (e.g., unifying participant naming; ensuring that times are coded as numeric)

```{r}
d <- d %>%
  #fix subject naming issue (now outdated)
  # mutate(sub_num = case_when(
  #    sub_num == "CAT-299" ~ "CAT_299",
  #    TRUE ~ sub_num
  #  )) %>%
  #ensure time is numeric (should already be the case)
  mutate(
    time=as.numeric(time),
    time_centered=as.numeric(time_centered)
  ) %>%
  #add frame count per trial
  group_by(sub_num,session,trial_order,trial_number) %>%
  # mutate(
  #   frame_count=n()
  # ) %>%
  #ensure trial number is numeric
  mutate(trial_number=as.numeric(trial_number)) %>%
  #add frame counter
  group_by(sub_num,session,trial_order,trial_number) %>%
  #this is a key part, since we will later use frame counter to generate corrected time
  #and to match up with the frame data generated during video concatenation
  mutate(
    #frame_counter_ns = seq(length(time)),
    frame_counter = skip_frames+seq(length(time)),
    total_frame_count = max(frame_counter)
  )

#slight renaming of order
d <- d %>%
  mutate(
    trial_order=str_replace(trial_order,"_","-")
  )
```

## Join in Subject information

```{r}
subj_all <- read_csv(processed_subj_path) 

#filter sessions greater than 2
subj <- subj_all %>%
  filter(session<=2)

#check unique subjects and looking data
#all coded looking file subject numbers have corresponding subject numbers in subj
setdiff(unique(d$sub_num),unique(subj$sub_num))
setdiff(unique(subj$sub_num),unique(d$sub_num))
#two participants in the subjects file don't have corresponding coded files
# [1] "CAT_228" "CAT_264"
# This makes sense:
# CAT_228 - no useable trials
# CAT_264 - did not code

#Do we also have corresponding sessions for all participants?
d_distinct_sessions <- d %>%
  ungroup() %>%
  distinct(sub_num,session,trial_order)

subj_distinct_sessions <- subj %>%
  ungroup() %>%
  distinct(sub_num,session,trial_order)

print(d_distinct_sessions %>% anti_join(subj_distinct_sessions))
print(subj_distinct_sessions %>% anti_join(d_distinct_sessions))
# Joining with `by = join_by(sub_num, session, trial_order)`
# # A tibble: 7 × 3
#   sub_num session trial_order         
#   <chr>     <dbl> <chr>               
# 1 CAT_218       1 order2B-locationflip
# 2 CAT_228       1 order1B             
# 3 CAT_242       1 order2A-locationflip
# 4 CAT_264       1 order1A-locationflip
# 5 CAT_264       2 order1B-locationflip
# 6 CAT_279       1 order2A-locationflip
# 7 CAT_332       1 order1B  

#CAT_218 1 --> not coded, infant too fussy, at best one useable trial
#CAT_228 1 --> no useable trials, stops very early
#CAT_242 1 --> not coded, infant too fussy, stops early and almost no useable trials
#CAT_264 1 --> did not code (parent interference)
#CAT_264 2 --> did not code (parent interference)
#CAT_279 1 --> did not code (not enough trials across sessions)
#CAT_332 1 --> did not code (too few trials)

d <- d %>%
  left_join(subj,by=c("sub_num","session","trial_order"))

#check join
distinct <- d %>%
  ungroup() %>%
  distinct(sub_num,session,trial_order,response_uuid)
```

## Integrate frame rate information to correct times

```{r}
#trials to keep
trials_to_keep <- c(11,12,13,14,16,17,18,19,21,22,23,24,26,27,28,29,31,32,33,34,36,37,38,39)
#list frame rate tables
fr_table_list <- list.files(path=frame_rate_info_path,pattern="txt")
#load and combine frame rate tables
fr_table <- map_df(fr_table_list,~mutate(read_delim(here::here(frame_rate_info_path,.),delim="\t"),file = str_replace(.,".txt",""))) %>%
  mutate(response_id=str_replace_all(file,pattern="framerate_table_","")) %>%
  #select only relevant trials
  filter(Trial %in% trials_to_keep) %>%
  #transform Trial to trial_num
  mutate(trial_number = Trial-10) %>%
  rename(response_uuid=response_id) 

#integrate with data
d <- d %>%
  left_join(fr_table) %>%
  clean_names() %>%
  mutate(
    frame_count_discrepancy = total_frame_count - framecount
  )
```

Check for cases where frame counts differ

```{r}
#inspect cases of discrepancy
hist(d$frame_count_discrepancy)
table(d$frame_count_discrepancy)
unusual_frame_count_trials <- d %>%
  distinct(file_name,sub_num,session,trial_number,total_frame_count,framecount,frame_count_discrepancy) %>%
  filter(abs(frame_count_discrepancy)>2)
#almost all frame counts are aligned with just a frame or two discrepancy
#remaining unusual frame counts confirmed as not an artifact
```

## Update times and accuracy coding

```{r}
d <- d %>%
  mutate(
    ms_per_frame = 1000/framerate,
    corrected_time = frame_counter * ms_per_frame,
    corrected_time_centered = corrected_time - 2650
  ) %>%
  mutate(accuracy_transformed = case_when(
    accuracy=="." ~ NA_integer_,
    TRUE ~ as.numeric(as.character(accuracy))))
```

## Incorporate timing info from Lookit

```{r}
#get frame data and extract trial number
frame_data <- read_csv(frame_data_path) %>%
  #exclude AG trials
  filter(!(trial_number %in% c(5,10,15,20,25))) %>%
  rename(trial_order=order_name,
         left_image_frame_info=left_image,
         right_image_frame_info=right_image)

#check to make sure frame data and looking data match for joining in
distinct_d_trials <- d %>%
  distinct(file_name,sub_num,session,response_uuid,child_hashed_id,trial_order,trial_number)
distinct_frame_data_trials <- frame_data %>%
  distinct(response_uuid,child_hashed_id,trial_order,trial_number)
#we should expect to have much fewer d trials (uncoded data)
print(distinct_frame_data_trials %>% anti_join(distinct_d_trials))
inspect_mismatches_frame_data <- distinct_frame_data_trials %>%
  left_join(select(subj_all,sub_num,session,response_uuid,child_hashed_id,trial_order)) %>%
  left_join(distinct_d_trials) %>%
  filter(is.na(file_name))
# all looks good - provides overview over not coded and/or prescreened trials
#but all looking data should have corresponding frame data
print(distinct_d_trials %>% anti_join(distinct_frame_data_trials))
#missing data from three trials - unclear why, but has minimal influence given limited scale

#join into data
d <- d %>%
  left_join(frame_data,by=c("response_uuid","child_hashed_id","trial_order","trial_number"))
fr_table_lookit <- frame_data %>%
  left_join(fr_table) %>%
  #filter(!is.na(child_hashed_id)) %>%
  mutate(
    estimated_time_framecount = 1000/Framerate*Framecount/1000,
    difference_video_trial_time=video_capture_time-estimated_time_framecount,
  )

#check join and order images
check_trial_orders <- d %>%
  ungroup() %>%
  distinct(sub_num,response_uuid,session,trial_order,trial_number,left_image,right_image,left_image_frame_info,right_image_frame_info) %>%
  mutate(
    left_image_frame_info_name = tools::file_path_sans_ext(left_image_frame_info),
    right_image_frame_info_name =tools::file_path_sans_ext(right_image_frame_info),
    left_image_frame_info_name_inv = right_image_frame_info_name,
    right_image_frame_info_name_inv =left_image_frame_info_name
  ) %>%
  mutate(
    left_image_mismatch = case_when(
      left_image!=left_image_frame_info_name_inv ~ 1,
      left_image==left_image_frame_info_name_inv ~ 0),
right_image_mismatch = case_when(
      right_image!=right_image_frame_info_name_inv ~ 1,
      right_image==right_image_frame_info_name_inv ~ 0),
    )
#all looks good!
```

We make a minor timing correction to account between lag between recording start and audio start, subtracting audio lag relative to video recording from our trial timer.

```{r}
d <- d %>%
  mutate(
    time_normalized_corrected = case_when(
      is.na(audio_lag_vs_video_s) ~ corrected_time_centered,
      TRUE ~ corrected_time_centered - audio_lag_vs_video_s*1000
    )
  )

# restrict data range
d <- d %>%
  filter(-3000<=time_normalized_corrected) %>%
  filter(7200>=time_normalized_corrected)
```

For reliability analysis: write out the frame ranges for relevant windows of analysis

```{r}
window_start <- -2000
window_end <- 2800

#relevant analysis window only
d_window <- d %>%
  filter(time_normalized_corrected>=window_start & time_normalized_corrected<=window_end)  
frame_range_d <- d_window %>%
  group_by(sub_num,session,trial_order,trial_number) %>%
  summarize(
    frame_count_start = min(frame_number),
    frame_count_end = max(frame_number)
  ) %>%
  mutate(
    filename = paste0(sub_num,"_session",session)
  )
write_csv(frame_range_d,here::here("..","..","data","processed_data","CATegories_analysis_window_frame_ranges.csv"))
```


## Join in typicality information

```{r}
## typicality
animal_rating_names <- read.csv(here::here("..","..","typicality_data","animal_ratings_stimuli_full.csv"))
animal_stims <- unique(c(unique(d$left_image),unique(d$right_image)))
typicality <- read.csv(here::here("..","..","typicality_data","typicality_animals_summarized.csv")) %>%
  mutate(item_name=str_remove(animal_name,pattern=" ")) %>%
  left_join(animal_rating_names) %>%
  mutate(image_name_resized = str_replace(image_experiment_name,".jpg","")) %>%
  filter(image_name_resized %in% animal_stims) %>%
  mutate(typicality_z=as.numeric(scale(mean_typicality))) %>%
  group_by(category) %>%
  mutate(typicality_within_category_z = as.numeric(scale(mean_typicality))) %>%
  ungroup()
#add typicality info
d <- d %>%
  left_join(typicality %>% select(image_name_resized,category,typicality_z,typicality_within_category_z),by=c("left_image" = "image_name_resized")) %>%
  rename(
    left_image_category=category,
    left_image_typicality_z=typicality_z,
    left_image_typicality_within_category_z=typicality_within_category_z) %>%
  left_join(typicality %>% select(image_name_resized,category,typicality_z,typicality_within_category_z),by=c("right_image" = "image_name_resized")) %>%
  rename(
    right_image_category=category,
    right_image_typicality_z=typicality_z,
    right_image_typicality_within_category_z=typicality_within_category_z) %>%
  mutate(
    target_category=case_when(
      target_side %in% c("right","R") ~ right_image_category,
      target_side %in% c("left","L") ~ left_image_category
    ),
    distractor_category=case_when(
      target_side %in% c("right","R") ~ left_image_category,
      target_side %in% c("left","L") ~ right_image_category
    ),
    target_typicality_z=case_when(
      target_side %in% c("right","R") ~ right_image_typicality_z,
      target_side %in% c("left","L") ~ left_image_typicality_z
    ),
    distractor_typicality_z=case_when(
      target_side %in% c("right","R") ~ left_image_typicality_z,
      target_side %in% c("left","L") ~ right_image_typicality_z
    ),
    target_typicality_within_category_z=case_when(
      target_side %in% c("right","R") ~ right_image_typicality_within_category_z,
      target_side %in% c("left","L") ~ left_image_typicality_within_category_z
    ),
    distractor_typicality_within_category_z=case_when(
      target_side %in% c("right","R") ~ left_image_typicality_within_category_z,
      target_side %in% c("left","L") ~ right_image_typicality_within_category_z
    ),
    target_image=case_when(
      target_side %in% c("right","R") ~ right_image,
      target_side %in% c("left","L") ~ left_image
    ),
    distractor_image=case_when(
      target_side %in% c("right","R") ~ left_image,
      target_side %in% c("left","L") ~ right_image
    )
  )
```

## Load survey data

```{r}
survey_data_long <- read_csv(survey_path)
```

## Join in survey rating

```{r}
#check sub_num overlap
setdiff(d$sub_num,survey_data_long$sub_num)
setdiff(survey_data_long$sub_num,d$sub_num)
d <- d %>%
  ungroup() %>%
  left_join(survey_data_long %>% select(sub_num,image_name,typical_num),by=c("sub_num","left_image" = "image_name")) %>%
  rename(left_image_parent_typicality_rating=typical_num) %>%
  left_join(survey_data_long %>% select(sub_num,image_name,typical_num),by=c("sub_num","right_image" = "image_name")) %>%
  rename(right_image_parent_typicality_rating=typical_num) %>%
  mutate(
    target_parent_typicality_rating=case_when(
      target_side %in% c("right","R") ~ right_image_parent_typicality_rating,
      target_side %in% c("left","L") ~ left_image_parent_typicality_rating
    ),
    distractor_parent_typicality_rating=case_when(
      target_side %in% c("right","R") ~ left_image_parent_typicality_rating,
      target_side %in% c("left","L") ~ right_image_parent_typicality_rating
    )
  ) %>%
  # add z-scored typicality
  left_join(survey_data_long %>% select(sub_num,image_name,typical_num_z),by=c("sub_num","left_image" = "image_name")) %>%
  rename(left_image_parent_typicality_rating_z=typical_num_z) %>%
  left_join(survey_data_long %>% select(sub_num,image_name,typical_num_z),by=c("sub_num","right_image" = "image_name")) %>%
  rename(right_image_parent_typicality_rating_z=typical_num_z) %>%
  mutate(
    target_parent_typicality_rating_z=case_when(
      target_side %in% c("right","R") ~ right_image_parent_typicality_rating_z,
      target_side %in% c("left","L") ~ left_image_parent_typicality_rating_z
    ),
    distractor_parent_typicality_rating_z=case_when(
      target_side %in% c("right","R") ~ left_image_parent_typicality_rating_z,
      target_side %in% c("left","L") ~ right_image_parent_typicality_rating_z
    )
  ) %>%
  #add parent typicality z-scored by category
  left_join(survey_data_long %>% select(sub_num,image_name,typical_by_category_z),by=c("sub_num","left_image" = "image_name")) %>%
  rename(left_image_parent_typicality_by_category_z=typical_by_category_z) %>%
  left_join(survey_data_long %>% select(sub_num,image_name,typical_by_category_z),by=c("sub_num","right_image" = "image_name")) %>%
  rename(right_image_parent_typicality_by_category_z=typical_by_category_z) %>%
  mutate(
    target_parent_typicality_by_category_z=case_when(
      target_side %in% c("right","R") ~ right_image_parent_typicality_by_category_z,
      target_side %in% c("left","L") ~ left_image_parent_typicality_by_category_z
    ),
    distractor_parent_typicality_by_category_z=case_when(
      target_side %in% c("right","R") ~ left_image_parent_typicality_by_category_z,
      target_side %in% c("left","L") ~ right_image_parent_typicality_by_category_z
    )
  )
```

## Add some exclusion-relevant columnns

Inspect information about child (based on child condition list column from Lookit) and update a "developmental concern" column accordingly.

```{r}
# inspect parent additional information
additional_info <- d %>%
  distinct(sub_num,child_condition_list) 

#add a column for developmental concern (no relevant participants identified based on info provided)
d <- d %>%
  mutate(
    dev_concern = case_when(
      #sub_num == "XXX" ~ "yes",
      TRUE ~ "no"
    )
  )
```

## Write the full dataset

```{r}
write_csv(d,write_path)
#also save as RDS object due to size
saveRDS(d,write_path_rds)
```

